doupi3

### 2023-02-02 outputs/paper.qmd
draft

# Introduction

# Data

## Data Source 
This report utilizes data on crime rates in Toronto neighborhoods obtained from the Toronto Police Service Annual Statistical Report (ASR) [@tpsasr]. The ASR is a comprehensive overview of police related statistics which has been openly available to the public since 2019 [@asr].

## Data Collection

## Data Characteristics

@@

## Data Analysis

@@

```{r}
#| echo: FALSE
#| warning: False
#| message: false
#| label: tab-meancrimerate

@@

kable(pivottable [-1,],
      col.names = c("Neighborhood Size",
                    "Small",
                    "Medium",
                    "Large",
                    "Giant"),
      caption = "Mean crime rate by neighborhood size in 2021",
      booktabs = TRUE, 
      longtable = TRUE
      ) |>
   kable_styling(bootstrap_options = c("hover", "condensed")) |>

@@

[insert something here]

@@

# Discussion

>>>>

# 1.Introduction

# 2.Data

## 2.1 Data Source

This report utilizes data on crime rates in Toronto neighborhoods obtained from the Toronto Police Service Annual Statistical Report (ASR) [@tpsasr]. The ASR is a comprehensive overview of police related statistics which has been openly available to the public since 2019 [@asr]. The neighborhood crime rate dataset analyzed in this report was obtained in csv format from the City of Toronto Open Data Portal using the R package `opendatatoronto` [@citeopendatatoronto]. The dataset was last updated on May 18th, 2022.

## 2.2 Data Collection

## 2.3 Data Characteristics

@@

## 2.4 Data Analysis

@@

```{r}
#| echo: FALSE
#| warning: False
#| message: false
#| label: tbl-meancrimerate
#| tbl-cap: "Mean crime rate by neighborhood size in 2021"

@@

kable(pivottable [-1,],
      col.names = c("Neighborhood Size",
                    "Small",
                    "Medium",
                    "Large",
                    "Giant"),
      booktabs = TRUE) |>
   kable_styling(bootstrap_options = c("hover", "condensed")) |>

@@

@@

# 3. Discussion
